--- 
title_meta  : Chapter 2
title       : Vectors
description : "In this free R course, we'll take you on a trip to Vegas, where you will learn how to analyze your gambling results using vectors in R! After completing this chapter, you will be able to create vectors in R, name them, select elements from them and compare different vectors."

--- type:NormalExercise xp:100 skills:1 key:d9b453dbdd
## Create a vector

Feeling lucky? You better, because this chapter takes you on a trip to the City of Sins, also known as *Statisticians Paradise*!

Thanks to R and your new data-analytical skills, you will learn how to uplift your performance at the tables and fire off your career as a professional gambler. This chapter will show how you can easily keep track of your betting progress and how you can do some simple analyses on past actions. Next stop, Vegas Baby... VEGAS!!

*** =instructions
- Do you still remember what you have learned in the first chapter? Assign the value `"Go!"` to the variable `vegas`. Remember: R is case sensitive!

*** =hint
Just type the following line in the editor:
```
vegas <- "Go!"
```

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Define the variable vegas
vegas <- 
```

*** =solution
```{r}
# Define the variable vegas
vegas <- "Go!"
```

*** =sct
```{r}
test_object("vegas", incorrect_msg = "Make sure that you assign the correct value to `vegas`. Do not forget that R is case sensitive!")
success_msg("Great! Head over to the next exercise.")
```
